Converting LaTeX Legacy R Journal Articles into R Markdown Articles using texor and rebib

### 2023-08-25 texor.Rmd
manual changes for new users given more detail

- Edit the lines where figures are included. <!--Why? What will need changing?-->
- Edit the tables. <!--If the simple conversion is insufficient?-->
- Include your R code, to dynamically do the computing described in your article.

>>>>

- Edit the lines where figures are included. The conversion will create HTML code to define the image. This should be changed into Markdown description `![Caption](Image)` or using `knitr::include_graphic(Image)` in an R code chunk, in order for both HTML and PDF versions of the paper to be created when the `rjtools` article template is knitted.  <!--Why? What will need changing?-->
- Edit the tables for aesthetics. The conversion will create Markdown tables, which will convert appropriately to HTML and PDF. However, to have more control and to create more elegant tables using `knitr::kable` provides finer level control. <!--If the simple conversion is insufficient?-->
- Include your R code, to dynamically do the computing described in your article. If any code block is time-consuming to complete, saving intermediate output, or caching would be recommended.

### 2023-08-25 texor.tex
software version numbers
manual changes for new users given more detail

\begin{itemize}
\tightlist
\item
  Edit the lines where figures are included.
\item
  Edit the tables.
\item
  Include your R code, to dynamically do the computing described in your article.
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  \CRANpkg{texor}: \url{https://abhi-1u.github.io/texor}
\item
  \CRANpkg{rebib}: \url{https://abhi-1u.github.io/rebib/}
\item
  This paper: \url{https://github.com/Abhi-1U/texor-rjarticle}
\item
  More details on \CRANpkg{rjtools} are at \url{https://rjournal.github.io/rjtools/}
\end{itemize}

>>>>

\begin{itemize}
\tightlist
\item
  Edit the lines where figures are included. The conversion will create HTML code to define the image. This should be changed into Markdown description \texttt{!{[}Caption{]}(Image)} or using \texttt{knitr::include\_graphic(Image)} in an R code chunk, in order for both HTML and PDF versions of the paper to be created when the \texttt{rjtools} article template is knitted.
\item
  Edit the tables for aesthetics. The conversion will create Markdown tables, which will convert appropriately to HTML and PDF. However, to have more control and to create more elegant tables using \texttt{knitr::kable} provides finer level control.
\item
  Include your R code, to dynamically do the computing described in your article. If any code block is time-consuming to complete, saving intermediate output, or caching would be recommended.
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  \CRANpkg{texor}: Version 1.2.0 \url{https://abhi-1u.github.io/texor}
\item
  \CRANpkg{rebib}: Version 0.3.0 \url{https://abhi-1u.github.io/rebib/}
\item
  This paper: \url{https://github.com/Abhi-1U/texor-rjarticle}
\item
  More details on \CRANpkg{rjtools} are at \url{https://rjournal.github.io/rjtools/}
\end{itemize}
